\section{Methodology}

\subsection{Empirical Setting and Event Definition}

The objective of this study is to decompose short-horizon price pressure into
economically distinct components—\emph{information-driven} and
\emph{liquidity-driven}—using market microstructure data. The empirical analysis
is conducted in an event-study framework centered on corporate earnings
announcements, which provide well-defined information events with well-documented
post-announcement return dynamics \citep{BallBrown1968,BernardThomas1989}.

For each earnings announcement, we define a pre-event measurement window of
trading days $[-10,-1]$ relative to the announcement date. All microstructure
features are constructed exclusively within this window. Post-event returns are
used solely for evaluation and play no role in feature construction or pressure
classification.

\subsection{Data Preprocessing}

\subsubsection{Trade--Quote Cleaning and Alignment}

Trades and quotes are cleaned using standard market microstructure filters
\citep{Hasbrouck2007}. Specifically, we remove trades with abnormal condition
codes, exclude quotes with zero or negative spreads, and eliminate locked or
crossed markets. Each trade is aligned to the prevailing NBBO using the most
recent valid quote prior to execution. This alignment is required for accurate
spread measurement and trade classification.

\subsection{Trade Classification and Order Flow Imbalance}

\subsubsection{Lee--Ready Trade Classification}

Trade direction is inferred using the Lee--Ready (1991) algorithm. Let $P_t$
denote the trade price and $M_t = (A_t + B_t)/2$ the contemporaneous midpoint of
the bid $B_t$ and ask $A_t$.

Trades are classified as:
\begin{itemize}
    \item buyer-initiated if $P_t > M_t$,
    \item seller-initiated if $P_t < M_t$,
    \item midpoint trades resolved using a tick-test fallback.
\end{itemize}

Despite known limitations at very high frequencies, the Lee--Ready algorithm
remains a standard benchmark for directional order flow estimation in equity
markets \citep{LeeReady1991,OddersWhite2000,Hasbrouck2007}.

\subsubsection{Daily Order Flow Imbalance}

Using classified trades, we compute daily order flow imbalance (OFI) as:
\begin{equation}
\text{OFI}_d = 
\frac{V^{\text{buy}}_d - V^{\text{sell}}_d}
     {V^{\text{buy}}_d + V^{\text{sell}}_d},
\end{equation}
where $V^{\text{buy}}_d$ and $V^{\text{sell}}_d$ denote buyer- and seller-initiated
traded volume on day $d$.

OFI captures net directional trading pressure and is closely related to the
theoretical concept of informed trading in \citet{Kyle1985} and the empirical
price impact literature \citep{Hasbrouck1991}. Normalization ensures
comparability across stocks and trading days.

\subsection{Liquidity and Spread Measures}

Liquidity conditions are measured using both quoted and effective spreads.
The quoted spread is defined as:
\begin{equation}
\text{QS}_d = \frac{A_d - B_d}{M_d},
\end{equation}
where $A_d$, $B_d$, and $M_d$ denote daily averages of the ask, bid, and midpoint.

The effective spread is computed as:
\begin{equation}
\text{ES}_d = 2 \times \frac{|P_t - M_t|}{M_t},
\end{equation}
averaged across trades.

Quoted spreads capture posted liquidity, while effective spreads capture realized
trading costs \citep{GlostenHarris1988}. Together, these measures allow us to
distinguish directional trading that occurs with minimal liquidity disruption
from trading associated with widening spreads and liquidity stress.

\subsection{Volume and Trading Intensity}

To capture trading intensity and potential liquidity shocks, we compute daily
share volume, dollar volume, and volume scaled by recent historical averages.
Abnormal volume episodes have long been associated with liquidity-driven price
pressure and temporary price dislocations
\citep{CampbellGrossmanWang1993}.

\subsection{Event-Level Feature Aggregation}

Daily microstructure measures are aggregated over the pre-announcement window
$[-10,-1]$ to form event-level summaries. Aggregation emphasizes economic
interpretability rather than statistical optimization.

Key constructs include:
\begin{itemize}
    \item \textbf{Order flow persistence}: Stability of OFI sign and magnitude
    across days, capturing gradual accumulation consistent with informed trading.
    \item \textbf{Spread stability}: Absence of systematic spread widening during
    periods of directional flow.
    \item \textbf{Volume irregularity}: Presence of large, transient volume spikes.
\end{itemize}

These constructs reflect the economic distinction between patient,
information-motivated trading and aggressive, liquidity-driven trading
\citep{Kyle1985,AdmatiPfleiderer1988}.

\subsection{Pressure Classification Framework}

For each event, we construct two latent scores:
\begin{itemize}
    \item an \emph{information pressure score}, increasing in order flow
    persistence and spread stability;
    \item a \emph{liquidity pressure score}, increasing in volume bursts and
    spread widening.
\end{itemize}

The final pressure score is defined as:
\begin{equation}
\text{Pressure}_i = \tanh(\text{InfoScore}_i - \text{LiqScore}_i),
\end{equation}
yielding a continuous measure bounded in $[-1, +1]$. Higher values indicate
information-dominated pressure, while lower values indicate liquidity-dominated
pressure. This formulation avoids arbitrary binary classification and aligns with
evidence that informed and liquidity trading coexist to varying degrees
\citep{Easley2012}.

\subsection{Latent Structure via Principal Component Analysis}

While the pressure score is constructed using economically motivated feature aggregation, it remains an empirical question whether the underlying feature space exhibits a structure consistent with the proposed distinction between information-driven and liquidity-driven trading. To address this, we apply principal component analysis (PCA) to the standardized event-level feature matrix.

Let $X \in \mathbb{R}^{N \times K}$ denote the matrix of standardized microstructure features, where $N$ indexes events and $K$ denotes the number of features. PCA decomposes the feature space as:
\begin{equation}
X = Z W',
\end{equation}
where $Z$ contains orthogonal principal components and $W$ contains the corresponding loadings.

Each principal component is a linear combination of the original features:
\begin{equation}
PC_j = X w_j,
\end{equation}
where $w_j$ is the eigenvector associated with the $j$-th largest eigenvalue of the covariance matrix of $X$.

\paragraph{Economic Interpretation.}
Rather than assigning economic meaning based on component ordering, we interpret principal components based on their loadings. In our implementation, components that load heavily on signed order flow and its persistence are interpreted as capturing information-driven trading, while components that load on spread variation and trading intensity are interpreted as capturing liquidity-related dynamics.

Importantly, the component most strongly associated with directional and persistent order flow emerges as a higher-order principal component rather than the first component. This highlights that information-driven trading is not the dominant source of variance in the data, but instead represents a more subtle and economically meaningful dimension of trading behavior.

\paragraph{Role of PCA.}
PCA serves two complementary purposes in our framework. First, it provides a data-driven decomposition of the feature space, allowing us to assess whether the hypothesized information-versus-liquidity structure is supported by the data. Second, it enables the construction of latent factors that can be used directly in predictive regressions.

Conceptually, the pressure score and PCA-based factors serve complementary roles. The pressure score provides an economically motivated and interpretable measure of trading pressure, while PCA offers a statistical decomposition of the same feature space. The consistency of results across these approaches strengthens the overall interpretation.

\subsection{Summary of Methodological Pipeline}

For clarity, the empirical procedure can be summarized as follows:
\begin{enumerate}
    \item Construct daily microstructure features from TAQ data.
    \item Aggregate features over the pre-announcement window to obtain event-level measures.
    \item Compute the pressure score based on economically motivated feature combinations.
    \item Apply PCA to the feature space to extract latent components.
    \item Map selected components to economically interpretable factors based on their loadings.
    \item Evaluate predictive power using cross-sectional regressions and event-study returns.
\end{enumerate}

This structure highlights the distinction between economically motivated construction (pressure score) and statistically derived factor extraction (PCA), as well as the complementary roles they play in the analysis.
