%========================================================
% Section 2: Data
%========================================================

\section{Data}

\subsection{Data Sources}

The empirical analysis combines high-frequency market microstructure data with
daily stock returns and corporate earnings announcement information. The primary
data sources are:

\begin{itemize}
    \item \textbf{WRDS TAQ (Trades and Quotes)}: Intraday transaction and National
    Best Bid and Offer (NBBO) quote data used to construct microstructure measures
    of order flow, liquidity, and trading intensity.
    \item \textbf{CRSP}: Daily stock returns, prices, shares outstanding, market
    capitalization, and trading volume.
    \item \textbf{Earnings announcement data}: Firm-level quarterly earnings
    announcement dates and timing used to define event windows.
\end{itemize}

These datasets are merged using standard security identifiers and calendar
alignment. All intraday TAQ data are processed locally; only aggregated daily
features are retained for analysis.

\subsection{Sample Construction}

The sample consists of U.S. common equities drawn from a large-cap universe over
the 2023--2024 period. To ensure reliable high-frequency measurement, we impose
liquidity filters requiring consistent daily trading activity and valid intraday
quote coverage. Securities with sparse trading, frequent trading halts, or
persistent data quality issues are excluded.

Earnings announcements are identified at the firm-quarter level. For each
announcement, we construct a pre-event measurement window of trading days
$[-10,-1]$ relative to the announcement date. Events are excluded if fewer than
ten valid trading days of TAQ data are available within the pre-event window.

The final sample comprises approximately several thousand earnings events across
hundreds of firms. The exact number of events varies slightly across
specifications due to data availability and filtering.

\subsection{Event and Return Windows}

Microstructure features are constructed exclusively using intraday data from the
pre-announcement window $[-10,-1]$. No post-announcement information is used in
feature construction or pressure classification.

Post-announcement returns are measured using CRSP daily returns over multiple
horizons, including short- and medium-term windows. These returns are used solely
for evaluation in event-study and cross-sectional regression analyses.

\subsection{Data Aggregation and Storage}

Intraday TAQ data are aggregated to daily stock-level features prior to event-level
processing. Daily features are then aggregated across the pre-event window to
construct event-level summaries.

To ensure transparency and reproducibility, all intermediate outputs are stored as
standalone datasets. Raw TAQ data are not included in the repository due to size
and licensing restrictions. The analysis relies exclusively on processed feature
files and documented aggregation procedures.

\subsection{Summary Statistics}

Table~\ref{tab:summary_stats} reports summary statistics for key daily
microstructure variables and event-level aggregates. Consistent with prior
microstructure studies, order flow imbalance exhibits substantial cross-sectional
and time-series variation, while spread and volume measures display significant
heterogeneity across securities and events.

Summary statistics are computed using the full sample of valid pre-announcement
observations and are reported to provide context for the magnitude and dispersion
of the constructed measures.
